A Context Menu for the Real World: Controlling Physical Devices Through Head-Worn Infrared Targeting

### 2013-09-16 doc/sigchi14/targeting.tex
add descriptions to charts
added strengths/shortcomings of IR

\bjoern{add more from survey answers}.

>>>>

\claire One noted benefit of IR mode was a feeling that it was \studyquote{more direct}. One subject appreciated the ability to \studyquote{interact with things just by looking at them}. Another mentioned that \studyquote{it's really convenient that what I'm looking at is what I'm targeting}.

\claire A perceived shortcoming of IR mode was the necessity to move the head in order to control a device. One participant said that it was \studyquote{awkward to be aiming your head at things, tweaking back and forth to get it right}. Another noted that observing the head movement didn't capture the site of her attention, because \studyquote {eye movement is an important part of how people look around}.
